### 2015-02-27 icfp15-servo/servo.tex
Move intrusive data structures into memory

@@

\subsection{Intrusive data structures}

Rust's ownership model assumes that there is a single owner for each piece of data.
However, many data structures do not follow that model, in order to provide asymptotic
improvements in access.
For example, a doubly-linked list contains a back pointer to the previous element to aid
in traversals in the opposite direction.
Many optimized hashtable implementations also have both hash-based access to items
and a linked list of all of the keys or values.

>>>>

Additionally, Rust's ownership model assumes that there is a single owner for each piece of data.
However, many data structures do not follow that model, in order to provide asymptotic
improvements in access.
For example, a doubly-linked list contains a back pointer to the previous element to aid
in traversals in the opposite direction.
Many optimized hashtable implementations also have both hash-based access to items
and a linked list of all of the keys or values.
In Servo, we have had to use unsafe code to implement data structures with this form,
though we are typically able to provide a safe interface to users.

@@
